Output Summary

### 2023-04-03 03-post-process/output-plots-children/13-post-vs-prior.Rmd
Improve Tau prior specification
Now each process has their own DF parameter

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_E_Pb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_lL_Pb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpi_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Pa_Mb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_lDelta_L_Pb_Mb_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Mb_Ma_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Ma_O0_prior`,`r jags_data$no`),`r jags_data$isw_df`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_O0_O1_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpsi_O1_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpsi_O2_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Rb_Ra_prior`,`r jags_data$no`),`r jags_data$isw_df`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Sb_Sa_prior`,`r jags_data$nj`),`r jags_data$isw_df`)`

>>>>

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_E_Pb_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lphi_E_Pb_prior[2]`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_lL_Pb_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_lL_Pb_prior[2]`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpi_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lpi_prior[2]`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Pa_Mb_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lphi_Pa_Mb_prior[2]`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_lDelta_L_Pb_Mb_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_lDelta_L_Pb_Mb_prior[2]`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Mb_Ma_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lphi_Mb_Ma_prior[2]`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Ma_O0_prior[1]`,`r jags_data$no`),`r jags_data$Tau_Lphi_Ma_O0_prior[2]`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_O0_O1_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lphi_O0_O1_prior[2]`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpsi_O1_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lpsi_O1_prior[2]`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lpsi_O2_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lpsi_O2_prior[2]`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Rb_Ra_prior[1]`,`r jags_data$no`),`r jags_data$Tau_Lphi_Rb_Ra_prior[2]`)`

@@

**Prior Used**: `dscaled.wishart(rep(`r jags_data$Tau_Lphi_Sb_Sa_prior[1]`,`r jags_data$nj`),`r jags_data$Tau_Lphi_Sb_Sa_prior[2]`)`
